Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-03-31 ProbabilisticCoherence.tex
Rewrote section 2, removed discussion of levels, changed title to hierarchical time series

\section{Notation}\label{sec:notation}

Our notation largely follows that introduced in \citet{Wickramasuriya2017}. Suppose $\bm{y}_t \in \mathbb{R}^n$ comprises all observations of the hierarchy at time $t$ and $\bm{b}_t \in \mathbb{R}^m$ comprises only the bottom-level observations at time $t$. Then due to the aggregation nature of the hierarchy we have
\begin{equation}
  \bm{y}_t = \bm{Sb}_t,
\end{equation}
where $\bm{S}$ is an $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold.

In any hierarchy, the most aggregated level is labelled level 0, the second most aggregated level is labelled level 1 and so on.

Consider the hierarchy given in Figure~\ref{fig1}.

@@

This example consists of two levels. At a particular time $t$, let $y_{Tot,t}$ denote the observation at level~0; $y_{A,t}, y_{B,t} $ denote observations at level~1; and $y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}$ denote observations at level~2. Then $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and 
$$ 
  \bm{S} = \begin{pmatrix} 
               1& 1 &1 &1  \\ 
               1 &1 & 0 &0 \\   
               0&0  & 1 & 1 \\ 
               & \multicolumn{2}{c}{I_4} &   
           \end{pmatrix}, 
$$ 
where $I_4$ is a $4$-dimension identity matrix.

>>>>

\section{Hierarchical Time Series}\label{sec:notation}

In the section, and throughout the paper, we will try to follow notational conventions used in \citet{Wickramasuriya2017} as much as possible.  A hierarchical time series is a collection of $n$ variables where some variables are aggregates of other variables.  For example in the hierarchy depicted in Figure~\ref{fig1} below, the variable labelled $Tot$ is the sum of the series $A$
and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.  The bottom level series are defined as those $m$ variables that cannot be formed as aggregates of other variables, in the example in Figure~\ref{fig1} these are the series $AA$, $AB$, $BA$ and $BB$.

@@

We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprised of observations of all variables in the hierarchy at time $t$,  and $\bm{b}_t \in \mathbb{R}^m$ is a vector comprised of observations of all bottom-level series at time $t$. The hierarchical structure of the data imply the following
\begin{equation}
  \bm{y}_t = \bm{Sb}_t,
\end{equation}
where $\bm{S}$ is an $n \times m$ constant matrix encoding the aggregation constraints.  For example for the hierarchy in Figure~\ref{fig1}, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and 
$$ 
  \bm{S} = \begin{pmatrix} 
               1& 1 &1 &1  \\ 
               1 &1 & 0 &0 \\   
               0&0  & 1 & 1 \\ 
               & \multicolumn{2}{c}{\bm{I}_4} &   
           \end{pmatrix}, 
$$

where $I_4$ is a $4$-dimension identity matrix.
